State of the Practice for Lattice Boltzmann Method Software

### 2022-04-23 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Further reduction of passive voice

We measured the total number of source code files for each project. We assume
that numerous source files is associated with increased reusability,
due to our assumption that this indicates increased modularization. Some
packages have more features than others.  This is assumed to contribute to
reusability, since they have more source code for potential reuse. The software
packages were also reviewed for the presence of API documentation, which
indicates that a software package was developed with interaction between other
software applications in mind.

@@

Table~\ref{moduledata} shows file and Lines Of Code (LOC) data for the software
packages. Packages with a high reusability score do not have as many LOC per
text file, generally having a few hundred lines or fewer. This suggests that the
source code of these packages is likely functionally modularized, and modules
could be reused in other projects.

The package waLBerla scored high on reusability because of its focus on
modularity.  The modularity in the waLBerla framework was included to enhance
productivity, reusability, and maintainability \citep{bauer2021walberla}. The
design of waLBerla has enabled it to be successfully applied in several projects
as a basis for various extensions \citep{bauer2021walberla}.

@@

Ten random source code files of each software package were reviewed for several
measures. This assessment of surface understandability may not perfectly reflect
each package, due to the practical limitation of only examining 10 files.

All the packages appear to have consistent indentation and formatting. Only
HemeLB, LUMA, and Musubi explicitly identify coding standards that are used
during development. Generally, the software packages use consistent,
distinctive, and meaningful code identifiers. Only four packages (LB2D-Prime,
LB3D-Prime, LIMBES, MP-LABS) appear to use vague identifiers, such as single
letters for variables. Symbolic constants were observed in the source code of 13
packages. The constants are used for various parameters, mathematical constants,
and matrix definitions. All the packages are reasonably well commented, with
the comments clearly indicating what is being done (as opposed to how it is
being done). Domain algorithms are noted in the source code of 11 packages.
Table~\ref{moduledata} suggests that the software packages are modularized to
various degrees. When observing the source code files, it was found that 14 of
the packages have a consistent style and order of function parameters.

>>>>

We measured the total number of source code files for each project. We assume
that numerous source files increases reusability, since more files implies
increased modularization. Some packages have more features than others.  This is
assumed to contribute to reusability, since they have more source code for
potential reuse. We reviewed the software packages for the presence of API
documentation, which suggests that the developers considered potential future
reuse.

@@

Table~\ref{moduledata} shows file and Lines Of Code (LOC) data for the software
packages. Packages with a high reusability score do not have as many LOC per
text file, generally having a few hundred lines or fewer. We assume that
relatively small files implies modularization.

The package waLBerla scored high on reusability because of its focus on
modularity.  The modularity in the waLBerla framework enhances productivity,
reusability, and maintainability \citep{bauer2021walberla}. The design of
waLBerla has enabled it to be successfully applied in several projects as a
basis for various extensions \citep{bauer2021walberla}.

@@

To measure understandability, we reviewed ten random source code files per
package.  By using only 10 files we may incorrectly estimate understandability,
but for practical consideration our time measuring each package has to be
limited.

All the packages appear to have consistent indentation and formatting. Only
HemeLB, LUMA, and Musubi explicitly identify coding standards that are used
during development. Generally, the software packages use consistent,
distinctive, and meaningful code identifiers. Only four packages (LB2D-Prime,
LB3D-Prime, LIMBES, MP-LABS) appear to use vague identifiers, such as single
letters for variables. Thirteen source code files used symbolic constants. The
constants are used for various parameters, mathematical constants, and matrix
definitions. All the packages are reasonably well commented, with the comments
clearly indicating what is being done (as opposed to how it is being done).
Domain algorithms are noted in the source code of 11 packages.
Table~\ref{moduledata} suggests that the software packages are modularized to
various degrees. When observing the source code files, it was found that 14 of
the packages have a consistent style and order of function parameters.
